% !TeX root = ../main.tex
% Add the above to each chapter to make compiling the PDF easier in some editors.

\chapter{Methodology}\label{chapter:methodology}

For the following chapters a systematic literature analysis according to the guidelines and the process model of Webster and Watson (2002) was carried out (Webster / Watson2002). The research relates to different terms or areas \hl{(XXX, XXX, XXX)}. First, different terms have been identified to cover different aspects of each chapter. Among other things, a search with a number of combinations of the relevant terms was completed for the individual chapters.
The databases used for the search provide a variety of publications, which is why a broad coverage of the terms is possible. The databases used for this work are as follows:

\begin{itemize}
    \item ACM Digital Library
    \item Google Scholar
    \item IEEE Xplore / Electronic Library Online (IEL)
    \item University Library of the Technical University of Munich
\end{itemize}

For the search results of the \hl{ first two chapters (XXX, XXX),} the following search criteria were used in meaningful combinations:

\begin{itemize}
    \item Enterprise Architecture
    \item Enterprise Architecture Management
    \item Automated documentation
    \item Cloud Computing
    \item \hl{...}
    
\end{itemize}

In addition, a backward search and a forward search were performed. This results in a larger total of results. Since the Technical University of Munich provides its students with a number of licenses, it is possible to use scientific research databases. The quality of the search results is ensured by the licenses for the databases and proves to be very helpful.
