% !TeX root = ../main.tex
% Add the above to each chapter to make compiling the PDF easier in some editors.

\chapter{Limitations}\label{chapter:conclusion}

This chapter describes the limitations emerged during this work.

\section{Technical challenges}
During the establishment of the prototype in the enterprise analyzed during the case study some technical challenges prevented an easy integration.

%Web-browser does not support ECMAScript 6
The first challenge was the web browser used in the company did not support ECMAScript 6. The visualizations implemented in the web component needed to be adapted to plain javascript.

%Server component adaptation for MySQL database component
The server component also needed some adaptations since the actual prototype uses a Nodejs server connected to a MongoDB database. This database was not supported by the enterprise so the server was adapted to be connected to a MySQL database. 

\section{Governance challenges}
After solving the technical challenges some governance challenges emerged that avoided a full cloud discovery. 

To accomplish a full discovery of the cloud environment and thus enable an EA documentation of the infrastructure, access rights to the whole environment needs to be guaranteed. This was not ensured therefore a complete discovery and EA documentation of the cloud infrastructure could not be fulfilled.

The integration of a pipeline script to enable an automated EAD of a new developed application was not tested in a pilot project due to time and governance constraints.
